### 2016-09-09 doc/publications/plos16/plos16.tex
added values to table

@@

\begin{table}[!ht]
\begin{minipage}{\textwidth}
\begin{adjustwidth}{-1.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{
{\bf Performance comparison between the different machine learning algorithms.}}
\begin{tabular}{|p{1.2cm}|p{1cm}|p{1.5cm}+l|l|p{1.8cm}|p{1.5cm}|}
\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
\bf{Data- set} & \bf{Samp- les} & \bf{Feat- ures}  & \bf{Method} & \bf{Error (ARI)} & \bf{Runtime} & \bf{Memory/ Node} \\
\hline
%\multirow{3}{*}{phase1\_chr22: 1,092 x 490,036} & CursedForest & 0.077 (XX)  &  &  \\
phase1 chr22 &1,092 & 490,036 & CursedForest & 0.077 (XX)  &  &  \\
&&& RF - Spark ML &  &  &  \\
&&& RF - R &  0.05  & 24 min  & 18GB\footnote{using the \texttt{parallel} packages with 10 nodes}\\
&&& ranger -R &         0.05 &        1 min 10 seconds  &          16GB  (one processor) \\
 \hline
phase3 chr22 & 2,504 & 1,103,548 &  &  &  &  \\
&&& RF - R & NA  & NA & NA\footnote{long vectors ($> 2^31-1$)  are not supported in the .Fortran interface}\\
&&&  H2O   &        0.05 &     16 hours       &   600GB \footnote{java -Xmx600g -jar h2o.jar,   h2o.init(nthreads=20)} \\
\hline
phase3 chr1 & 2,504 & 6,450,364 & CursedForest & 0.063 (XX) & 1hr 58min & 4GB \\
&&& RF - Spark ML & 0.94 & 8hr 29min & 8GB \\
&&& LR - Spark ML&  & 2hr 6min & 8GB\\ 
&&& ranger  R   &  0.06   &     28 mins  &            num.threads = 10\footnote{don't know how to get the memory used, This
  was done on dpas-03} \\ 
\hline
phase3 chr1-3 & 2,504 & 19,328,051  & CursedForest & 0.046 (XX) & 4hr 0min & 4GB\\
&&& RF - Spark ML & &  &\\
&&& LR - Spark ML & & 14hr 48min & 8GB \\ 
&&& ranger  R   &  0.05   &     58 mins\footnote{ but took 6 hours to load the data}  &      909GB\footnote{I think this is total memory. The job was run with
  ntasks-per-node=160 cores-per-socket=10 on ruby }  \\ 
\hline
phase3 chr1-22 & 2,504 & 81,047,467 & CursedForest & XX (0.96) & 7hr 14min & 8GB \\ 
&&& RF - Spark ML & - & - & - \\
&&& LR - Spark ML & - & - & - \\ 
%&&& kmeans - Spark ML & - (0.82) & 30hr 44min & 24GB \\ 
\hline
\end{tabular}
\begin{flushleft} 
Comparison of different various machine learning libraries on different subsets of variant data 
from the 1000 Genomes Project. 
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{minipage}
\end{table}

>>>>

\usepackage{footmisc}

@@

\begin{table}[!ht]
\begin{minipage}{\textwidth}
\begin{adjustwidth}{-1.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{
{\bf Performance comparison between the different machine learning algorithms.}}
\begin{tabular}{|p{1.2cm}|p{1cm}|p{1.5cm}+l|l|p{1.8cm}|p{1.5cm}|}
\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
\bf{Data- set} & \bf{Samp- les} & \bf{Feat- ures}  & \bf{Method} & \bf{Error (ARI)} & \bf{Runtime} & \bf{Memory/ Node} \\
\hline
%\multirow{3}{*}{phase1\_chr22: 1,092 x 490,036} & CursedForest & 0.077 (XX)  &  &  \\
phase1 chr22 &1,092 & 490,036 & CursedForest & 0.077 (XX)  & 9min 16sec & 1GB\footnote{\label{note10}10 nodes} \\
&&& RF - Spark ML & 0.069 (0.89) & 14min 13sec & 1GB\footref{note10}  \\
&&& RF - R &  0.05  & 24min  & 18GB\footref{note1}\footnote{using the \texttt{parallel} packages}\\
&&& ranger -R &         0.05 &        1min 10sec  &          16GB  (one processor) \\
 \hline
phase3 chr22 & 2,504 & 1,103,548 &  &  &  &  \\
&&& CursedForest & 0.053 & 9 min 8 sec & 2GB\footnote{\label{note20}20 nodes}\\
&&& RF - Spark ML & 0.058 (0.92) & 1hr 1min & 2GB\footref{note20} \\
&&& RF - R & NA  & NA & NA\footnote{long vectors ($> 2^31-1$)  are not supported in the .Fortran interface}\\
&&&  H2O   &        0.05 &     16 hours       &   600GB \footnote{java -Xmx600g -jar h2o.jar,   h2o.init(nthreads=20)} \\
\hline
phase3 chr1 & 2,504 & 6,450,364 & CursedForest & 0.063 (XX) & 1hr 58min & 4GB \\
&&& RF - Spark ML & (0.94) & 8hr 29min & 8GB \\
&&& LR - Spark ML&  & 2hr 6min & 8GB\\ 
&&& ranger  R   &  0.06   &     28 mins  &            num.threads = 10\footnote{don't know how to get the memory used, This
  was done on dpas-03} \\ 
\hline
phase3 chr1-3 & 2,504 & 19,328,051  & CursedForest & 0.046 (XX) & 4hr 0min & 4GB\\
&&& RF - Spark ML & - & -  & -\\
&&& LR - Spark ML & & 14hr 48min & 8GB \\ 
&&& ranger  R   &  0.05   &     58 mins\footnote{ but took 6 hours to load the data}  &      909GB\footnote{I think this is total memory. The job was run with
  ntasks-per-node=160 cores-per-socket=10 on ruby }  \\ 
\hline
phase3 chr1-22 & 2,504 & 81,047,467 & CursedForest & XX (0.96) & 7hr 14min & 8GB \\ 
&&& RF - Spark ML & - & - & - \\
&&& LR - Spark ML & - & - & - \\ 
%&&& kmeans - Spark ML & - (0.82) & 30hr 44min & 24GB \\ 
\hline
\end{tabular}
\begin{flushleft} 
Comparison of different various machine learning libraries on different subsets of variant data 
from the 1000 Genomes Project.
Each random forest model consists of 50 trees.
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{minipage}
\end{table}
